### 2022-11-15 NSF2022/Description/backgroundv3.tex
...

The field of self-organization encompasses a broad range of interesting
and challenging phenomena in engineering and science. For example,
understanding the organization of lipids and proteins in vesicles is
crucial to designing effective drug carriers and functional mimics of
cells~\cite{Marui2022IncreasedEO,
https://doi.org/10.1002/adma.202206288}. The COVID-19 pandemic has led
to a concerted effort to understand the mechanisms of RNA condensation
by structural proteins that control virus
structure~\cite{Kim2021SelfassembledMV}. Engineers develop superior
techniques that rely on nanoscale capillary and van der Waals forces to
print high-resolution features on devices~\cite{Zeng20223DprintedMT}.
Finally, researchers design efficient algorithms for constructing
interaction kernels in the to study of agent-based systems like swarms
and flocking~\cite{Lu2019NonparametricIO, Tadmor2021OnTM}.

@@

When fluids are involved, tracking self-organization becomes difficult
due to the deformability of suspended media in the presence of non-local
hydrodynamic interactions. The phase field method, a prominent approach
in this area, introduces a scalar-valued phase field function for the
volume fraction of amphiphilic lipids or polymers in solvent, for
example. Sometimes called the diffuse interface method, one devises
energy functionals involving the gradient and well-potentials of the
phase field, and possibly convolution kernels, to characterize the self-
and solvent-interaction of the suspended
media~\cite{Promislow2022UndulatedBI, C9SM01983A,doi:10.1063/5.0009734,
LiAn-Chang16, Choksi2003OnTD}. Because the fluid interfaces are given by
level-sets of a smooth function, they can have almost arbitrary topology
such as free ends and junctions~\cite{Promislow2017ExistenceBA,
Promislow2022UndulatedBI}, the evolution equations can be studied by
well-established variational and analytical
tools~\cite{Gavish2011CurvatureDF, Dai2019WeakSF, Dai2015CompetitiveGE,
Dai2022GeometricEO, Dai2020MinimizersFT, Dai2013GeometricEO}, and the
governing equations are amenable to numerical
approximation~\cite{Christlieb2020BenchmarkCO,
Christlieb2019CompetitionAC}. One of the downsides, though, is that
granular details like molecular heterogeneity and orientations that may
be crucial to the physics at mesoscopic scales \cite{Midya2022}, are blurred
by the model. Moreover, numerical simulations of phase field
models typically discretize the entire fluid domain, and apply cutoff
boundary conditions when periodic domains are not under consideration.

The PIs recently developed a new mathematical model of self-organization
in fluid systems~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM}. The
framework uses small, rigid bodies called ``granules'' to represent
parcels of suspended media. The granule shapes and boundary conditions
capture the local properties of the suspension, and instead of volume
fraction, a phase field function represents the properties of the
solvent. Our approach falls into the category of work that considers
particles as a discretization of a continuous problem; in this case one
is dealing with a particle method, as an alternative to other
stencil-based discretization methods~\cite{Wilson2021ComparisonOT,Gross2020MeshfreeMO,
Sigurdsson2016HydrodynamicCO}.
We have departed from the terminology ``particles'', though,
to emphasize the role played elliptic equations and the granules'
finite size.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize (a) The moving domain,
  $\Omega(t)$, of granules with centers $\aa_i$, directors $\dd_i$ with
  $|\dd_i| = 1$, and the unit inward normal $\nnu$. Panels (b), (c), (d)
  show the interplay between the phase field $\phi$ (colormap) and
  granule configuration. Red is for $\phi = 1$ and blue for $\phi = 0$;
  $W(\phi) = \tfrac{1}{2}\phi^2$. The white arrows are the fluid
  velocity field. The panels reach an equilibrium state in panel (d).}
\end{figure}

@@

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of a continuous, permeable, inextensible,
elastic vesicle. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading
vesicle~\cite{Finken2008, Shaqfeh11} (Figure~\ref{fig:JPv_linearshear}).
Movies of Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction are in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure~\ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear
rate~\cite{VLAHOVSKA2009775, keller_skalak_1982}. A side-by-side
comparison of granule-based vesicles and the sharp interface
representation yields shapes and trajectories that basically overlap.

>>>>

The field of self-organization encompasses a broad range of interesting
and challenging phenomena in engineering and science. For example,
understanding the organization of lipids and proteins in vesicles is
crucial to designing effective drug carriers and functional mimics of
cells~\cite{Marui2022IncreasedEO,
https://doi.org/10.1002/adma.202206288}. The COVID-19 pandemic has led
to a concerted effort to understand the mechanisms of RNA condensation
by structural proteins that control virus
structure~\cite{Kim2021SelfassembledMV}. Engineers develop superior
techniques that rely on nanoscale capillary and van der Waals forces to
print high-resolution features on devices~\cite{Zeng20223DprintedMT}.
Finally, researchers design efficient algorithms for constructing
interaction kernels to study agent-based systems like swarms
and flocking~\cite{Lu2019NonparametricIO, Tadmor2021OnTM}.

@@

When fluids are involved, tracking self-organization becomes difficult
due to the deformability of suspended media in the presence of non-local
hydrodynamic interactions. The phase field method, a prominent approach
in this area, introduces a scalar-valued phase-field function for the
volume fraction of amphiphilic lipids or polymers in solvent, for
example. Sometimes called the diffuse interface method, one devises
energy functionals involving the gradient and well-potentials of the
phase field, and possibly convolution kernels, to characterize the self-
and solvent-interaction of the suspended
media~\cite{Promislow2022UndulatedBI, C9SM01983A,doi:10.1063/5.0009734,
LiAn-Chang16, Choksi2003OnTD}. Because the fluid interfaces are given by
level-sets of a smooth function, they can have almost arbitrary topology
such as free ends and junctions~\cite{Promislow2017ExistenceBA,
Promislow2022UndulatedBI}, the evolution equations can be studied by
well-established variational and analytical
tools~\cite{Gavish2011CurvatureDF, Dai2019WeakSF, Dai2015CompetitiveGE,
Dai2022GeometricEO, Dai2020MinimizersFT, Dai2013GeometricEO}, and the
governing equations are amenable to numerical
approximation~\cite{Christlieb2020BenchmarkCO,
Christlieb2019CompetitionAC}. One of the downsides, though, is that
granular details like molecular heterogeneity and orientations that may
be crucial to the physics at mesoscopic scales \cite{Midya2022}, are blurred
by the model. Moreover, numerical simulations of phase field
models typically discretize the entire fluid domain, and apply cutoff
boundary conditions when periodic domains are not under consideration.

The PIs recently developed a new mathematical model of self-organization
in fluid systems~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM}. The
framework uses small, rigid bodies called ``granules'' to represent
parcels of suspended media. The granule shapes and boundary conditions
capture the local properties of the suspension, and instead of volume
fraction, a phase field function represents the properties of the
solvent. Our approach falls into the category of work that considers
particles as a discretization of a continuous problem; in this case one
is dealing with a particle method, as an alternative to other
stencil-based discretization methods~\cite{Wilson2021ComparisonOT,Gross2020MeshfreeMO,
Sigurdsson2016HydrodynamicCO}.
We have departed from the terminology ``particles'', though,
to emphasize the role played by elliptic equations and the granules'
finite size.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize (a) The moving domain,
  $\Omega(t)$, of granules with centers $\aa_i$, directors $\dd_i$ with
  $|\dd_i| = 1$, and the unit inward normal $\nnu$. Panels (b), (c), (d)
  show the interplay between the phase field $\phi$ (colormap) and
  granule configuration. Red is for $\phi = 1$ and blue for $\phi = 0$;
  $W(\phi) = \tfrac{1}{2}\phi^2$. The white arrows are the fluid
  velocity field. The granules reach an equilibrium state in panel (d).}
\end{figure}

@@

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of a continuous, permeable, inextensible,
elastic vesicle. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading
vesicle~\cite{Finken2008, Shaqfeh11} (Figure~\ref{fig:JPv_linearshear}).
Movies of Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction are in good quantitative
agreement with those derived by atomistic and Martini force field simulation
studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure~\ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear
rate~\cite{VLAHOVSKA2009775, keller_skalak_1982}. A side-by-side
comparison of granule-based vesicles and the sharp interface
representation yields shapes and trajectories that basically overlap.

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
...

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates variational techniques and offers
insight into fundamentals of self-organization and collective dynamics.
The project brings socially consequential research into the classroom
and offers undergraduates the opportunity to train alongside faculty and
graduate students. With its unique combination of mathematical modeling,
analysis, and scientific computing, the project highlights the potential
advancement of STEM from Applied Mathematics.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences, the proposal supports two
summer undergraduate researchers (URs) per year at Fordham University for
eight weeks. The URs will collaborate directly with the PIs,
receive tutorials (e.g., numerical methods), and be guided on
mathematical writing and presentation. Fordham Mathematics recently
completed a collaboration studio purpose-built for UR support. Work
products include a summary manuscript, a presentation in the Fordham
Undergraduate Research Symposium and departmental seminars, and
participation in a national conference. We have outlined three projects
for the present proposal:
\begin{enumerate}[noitemsep,topsep=0pt]
  \item Translate project code from MATLAB into a compiled language;
  \item Use machine learning and visualizations to post-process data of
    granule dynamics;
  \item Mathematical modeling of collective behavior in social sciences.
\end{enumerate}
PI Ryham has worked side-by-side with dozens of undergraduates and
high-schoolers in supported summer research, Girls in Science Technology
and Mathematics, and the Clare Boothe Luce Scholarship program and the
activity benefited their careers in machine learning, water resources
engineering, threat detection, and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on polling
accessibility in New York City. The PI is finishing works on energy
densities for lipid bilayers with a recently graduated UR, now working
at Raytheon Technologies. His publications include works with seven
undergraduate coauthors~\cite{Figueroa2012CuttingCI, RYHAM20112929,
RyWaCo13, RyKlYaCo16}.

>>>>

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates variational techniques and offers
insight into fundamentals of self-organization and collective dynamics.
The project brings socially consequential research into the classroom
and offers undergraduates the opportunity to train alongside faculty and
graduate students. With its combination of mathematical modeling,
analysis, and scientific computing, the project highlights the potential
advancement of STEM from Applied Mathematics.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences, the proposal supports two
summer undergraduate researchers (URs) per year at Fordham University for
eight weeks. The URs will collaborate directly with the PIs,
receive tutorials (e.g., on numerical methods), and be guided on
mathematical writing and presentation. Fordham Mathematics recently
completed a collaboration studio purpose-built for UR support. Work
products include a summary manuscript, a presentation in the Fordham
Undergraduate Research Symposium and departmental seminars, and
participation in a national conference. We have outlined three projects
for the present proposal:
\begin{enumerate}[noitemsep,topsep=0pt]
  \item Translate project code from MATLAB into a compiled language;
  \item Use machine learning and visualizations to post-process data of
    granule dynamics;
  \item Mathematical modeling of collective behavior in social sciences.
\end{enumerate}
PI Ryham has worked side-by-side with dozens of undergraduates and
high-schoolers in supported summer research, Girls in Science Technology
and Mathematics, and the Clare Boothe Luce Scholarship program and the
activity benefited their careers in machine learning, water resources
engineering, threat detection, and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on polling
accessibility in New York City. The PI is finishing works on energy
densities for lipid bilayers with a recently graduated UR, now working
at Raytheon Technologies. His publications include works with seven
undergraduate coauthors~\cite{Figueroa2012CuttingCI, RYHAM20112929,
RyWaCo13, RyKlYaCo16}.

### 2022-11-15 NSF2022/Description/specificaim1v2.tex
...

The first step is to obtain some solid well-posedness results
for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an
autonomous system of ordinary differential equations (ODEs) for the body
transformations $\FF_i$ with the rate of change defined by a system of
PDEs. Strategies have been proposed for the solution of coupled PDE/ODE
systems \cite{Carichino2018EnergybasedOS,Quarteroni2016GeometricMM}.
Regarding \eqref{eq:RBT}--\eqref{eqn:stressbalance}, in the linear case
and for fixed $t$, there is a unique solution ($\phi, \uu$) under
appropriate assumptions for the boundaries and boundary
data~\cite{manasthesis, rac-gre2016, LAX}. These define instantaneous
rigid body velocities and rotations, leading to the following problem.
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection of closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and smooth
  phase field boundary conditions. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we must
establish that the system has a local-in-time solution. This involves
domain perturbations and estimates for the solutions of second-order
elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example.
For global-in-time solutions, we can use lubrication
forces~\cite{cawthorn_balmforth_2010, leal_2007}. Here, the lubrication
force required to bring granules into contact blows up with distance,
and we must analyze whether the attraction~\eqref{eqn:stressbalance}
stays finite in order to guarantee positivity in the distance between
granules.
Finally, we can study the granule-flow behavior in the
zero-decay length limit. This limit should recover the hydrodynamics of
a (noninteracting) rigid-body suspension.

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under an amphiphilic boundary condition. (a)
  Granules first match hydrophobic tails (red), (b) then align
  lengthwise. (c) The same pattern of self-organization holds in three
  dimensions, as simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g., granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF}.
To have one solution $\phi$ for each $t$, 
we must reformulate~\eqref{eqn:phase} as
the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\beta \frac{\delta E}{\delta \phi}
  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an additional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI, Gera2017CahnHilliardOS}
and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematic liquid crystals concerns the interaction of Landau-de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple colloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
Alama2021SaturnRD, PhysRevE.96.042702}.
PI Ryham has several works on
membrane vesicles dealing both with Allen-Cahn formulations and
fluid-vesicle interactions~\cite{QiangDu09, RYHAM20112929, RyCoEi12,
Ryham2017OnTV}.

@@

\begin{quotation}
  \noindent
  \textbf{Problem 2.}
  Consider a collection of two-dimensional amphiphilic granules along a
  closed curve $\mathcal{C}$. What is the sharp interface limit of the
  energy $E$ as the number of granules goes to infinity and their size
  to zero?
\end{quotation}
Sharp interface models represent a membrane vesicle as an
inextensible, continuous, closed surface $\Sigma$ with elastic energy
\begin{align}
  \label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS,
\end{align}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
$k_B$ is a bending modulus. One can also account
for spatially dependent spontaneous curvature
\cite{PhysRevE.79.031926,Lowengrub13,mahapatra_saintillan_rangamani_2020}
and for extensibility by
including in~\eqref{eq:Canham-Helfrich} an additional stretching term
$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
the deformed and equilibrium area densities respectively
\cite{chabanon2017}, and $k_A$ is a stretching modulus.

>>>>

The first step is to obtain some solid well-posedness results
for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an
autonomous system of ordinary differential equations (ODEs) for the body
transformations $\FF_i$ with the rate of change defined by a system of
PDEs. Strategies have been proposed for the solution of coupled PDE/ODE
systems \cite{Carichino2018EnergybasedOS,Quarteroni2016GeometricMM}.
Regarding \eqref{eq:RBT}--\eqref{eqn:stressbalance}, in the linear case
and for fixed $t$, there is a unique solution ($\phi, \uu$) under
appropriate assumptions for the boundaries and boundary
data~\cite{manasthesis, rac-gre2016, LAX}. These define instantaneous
rigid body velocities and rotations, leading to the following problem.
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection of closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and smooth
  phase field boundary conditions. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we must
establish that the system has a local-in-time solution. This involves
domain perturbations and estimates for the solutions of second-order
elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example.
For global-in-time solutions, we can use lubrication
forces~\cite{cawthorn_balmforth_2010, leal_2007}. Here, the lubrication
force required to bring granules into contact blows up with distance,
and we must analyze whether the attraction~\eqref{eqn:stressbalance}
stays finite in order to guarantee positivity in the distance between
granules with respect to time.
Finally, we can study the granule-flow behavior in the
zero-decay length limit. This limit should recover the hydrodynamics of
a (noninteracting) rigid-body suspension.

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under an amphiphilic boundary condition. (a)
  Granules first match hydrophobic tails (red), (b) then align
  lengthwise. (c) The same pattern of self-organization holds in three
  dimensions, as simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g., granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF}.
To have one solution $\phi$ for each $t$, 
we must reformulate~\eqref{eqn:phase} as
the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla \phi
  = -\zeta \frac{\delta E}{\delta \phi}
  = \zeta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an additional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\zeta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI, Gera2017CahnHilliardOS}
and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematic liquid crystals concerns the interaction of Landau-de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple colloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
Alama2021SaturnRD, PhysRevE.96.042702}.
PI Ryham has several works on
membrane vesicles dealing both with Allen-Cahn formulations and
fluid-vesicle interactions~\cite{QiangDu09, RYHAM20112929, RyCoEi12,
Ryham2017OnTV}.

@@

\begin{quotation}
  \noindent
  \textbf{Problem 2.}
  Consider a collection of two-dimensional amphiphilic granules along a
  closed curve $\mathcal{C}$. What is the sharp interface limit of the
  energy $E$ as the number of granules goes to infinity and their size
  to zero?
\end{quotation}
Sharp interface models represent a membrane vesicle as an
inextensible, continuous, closed surface $\Sigma$ with elastic energy
\begin{align}
  \label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS,
\end{align}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
$k_B$ is a bending modulus. One can also account
for spatially dependent spontaneous curvature
\cite{PhysRevE.79.031926,Lowengrub13,mahapatra_saintillan_rangamani_2020}
and for extensibility by
including in~\eqref{eq:Canham-Helfrich} an additional stretching term
$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
the deformed and equilibrium area densities, respectively
\cite{chabanon2017}, and $k_A$ is a stretching modulus.

### 2022-11-15 NSF2022/Description/specificaim2.tex
...

As an illustration, the problem of finding the global electrostatic
potential $u$ with surface charge density $\sigma$ is a special case
of~\eqref{eqn:conv}, where $G(\xx - \yy)$ takes the form $-(2\pi
\epsilon_0)^{-1}\log|\xx - \yy|$ in two dimensions and $(4\pi
\epsilon_0)^{-1}|\xx -\yy|^{-1}$ in three dimensions with $\epsilon_0$
the permittivity in a vacuum. In this context, equation~\eqref{eqn:bie}
is analogous to Gauss's Law.

The PIs have demonstrated that IEs are a powerful tool to simulate
two-dimensional suspensions of amphiphilic particles~\cite{Fu2018_SIAM,
FuQuRyYo22, fu-ryh-qua-you2022}, and elements of these formulations have
been developed in three dimensions~\cite{ying_2006, manasthesis,
rac-gre2016}. In our current implementation, we simulate
$\mathcal{O}(100)$ two-dimensional granules, and the proposed research
will allow for the suspensions with 100X--1000X more two-dimensional
granules and $\mathcal{O}(1000)$ three-dimensional granules.

@@

\begin{wrapfigure}[17]{r}{1.9in}
  \vspace{-4pt}
  \centering
  \input{figures/near_sing.tikz}
  \vspace{-15pt}
  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
  quadrature method that works in two and three dimensions. The accurate
  trapezoid rule is used in points in $\mathtt{Far}(\Gamma_i)$, while
  one dimensional interpolant is used for points in
  $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength spacing.}
\end{wrapfigure}
Since we are interested in round (2D) and spherical (3D) granules, we
will exploit the fact that integrals can be computed with spectral
accuracy by transforming the integrals to a Fourier (2D) or spherical
harmonic (3D) basis. This technique can be used to evaluate layer
potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
appropriate or other shapes, and an alternative approach is necessary.
The Barycentric-type formulae for Cauchy integrals results in a
uniformly bounded quadrature error, but the method is described only for
the two-dimensional Laplace and Stokes equations. PI Quaife recently
showed that these quadrature methods can be extended to other
two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
singularity subtraction to write the fundamental solution of the PDE as
a sum of two terms: a logarithmic function and a continuously
differentiable remainder. Then the Barycentric-type formulae can be
applied to the logarithmic function, and the standard trapezoid
rule~\cite{tre-wei2014} can be applied to the remainder. These
singularity subtraction methods can also accurately compute derivatives
of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
required, for example, when computing the phase
stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
also be applied in three dimensions, but not combined with
Barycentric-type formulae. Alternatively, smoothed variations of the
fundamental solution can be used to address nearly-singular
integrals~\cite{beale1, cor2001, tlu-bea2019}. Finally, efficient
quadrature methods can be applied directly to accurately compute
singular and near-singular integrals~\cite{khayat_2005,
gimbutas2013sisc}.

>>>>

As an illustration, the problem of finding the global electrostatic
potential with surface charge density $\sigma$ is a special case
of~\eqref{eqn:conv}, where $G(\xx - \yy)$ takes the form $-(2\pi
\epsilon_0)^{-1}\log|\xx - \yy|$ in two dimensions and $(4\pi
\epsilon_0)^{-1}|\xx -\yy|^{-1}$ in three dimensions with $\epsilon_0$
the permittivity in a vacuum. In this context, equation~\eqref{eqn:bie}
is analogous to Gauss's Law.

The PIs have demonstrated that IEs are a powerful tool to simulate
two-dimensional suspensions of amphiphilic particles~\cite{Fu2018_SIAM,
FuQuRyYo22, fu-ryh-qua-you2022}, and elements of these formulations have
been developed in three dimensions~\cite{ying_2006, manasthesis,
rac-gre2016}. In our current implementation, we simulate
$\mathcal{O}(100)$ two-dimensional granules, and the proposed research
will allow for the suspensions with 100--1000 times more two-dimensional
granules and $\mathcal{O}(1000)$ three-dimensional granules.

@@

\begin{wrapfigure}[17]{r}{1.9in}
  \vspace{-4pt}
  \centering
  \input{figures/near_sing.tikz}
  \vspace{-15pt}
  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
  quadrature method that works in two and three dimensions. The accurate
  trapezoid rule is used in points in $\mathtt{Far}(\Gamma_i)$, while
  one dimensional interpolant is used for points in
  $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength spacing.}
\end{wrapfigure}
Since we are interested in round (2D) and spherical (3D) granules, we
will exploit the fact that integrals can be computed with spectral
accuracy by transforming the integrals to a Fourier (2D) or spherical
harmonic (3D) basis. This technique can be used to evaluate layer
potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
appropriate for other shapes, and an alternative approach is necessary.
The Barycentric-type formulae for Cauchy integrals results in a
uniformly bounded quadrature error, but the method is described only for
the two-dimensional Laplace and Stokes equations. PI Quaife recently
showed that these quadrature methods can be extended to other
two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
singularity subtraction to write the fundamental solution of the PDE as
a sum of two terms: a logarithmic function and a continuously
differentiable remainder. Then the Barycentric-type formulae can be
applied to the logarithmic function, and the standard trapezoid
rule~\cite{tre-wei2014} can be applied to the remainder. These
singularity subtraction methods can also accurately compute derivatives
of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
required, for example, when computing the phase
stress $T_i$ in equation~\eqref{eqn:hydro_stress}. Singularity subtraction methods can
also be applied in three dimensions, but not combined with
Barycentric-type formulae. Alternatively, smoothed variations of the
fundamental solution can be used to address nearly-singular
integrals~\cite{beale1, cor2001, tlu-bea2019}. Finally, efficient
quadrature methods can be applied directly to accurately compute
singular and near-singular integrals~\cite{khayat_2005,
gimbutas2013sisc}.
